Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-08-12 Manuscript/supplemental.tex

\section*{Appendix B: Supplementary information on visitation}

@@

\section*{Appendix C: Supplementary information on models}

@@

\subsection*{Commodity canola model coefficients}

@@

@@

\subsection*{Seed canola model coefficients}

@@

@@

>>>>

\section*{Appendix B: Additional information on insect visitors}

@@

\section*{Appendix C: Additional information on models}

@@

@@

\caption{Summary of parameters for commodity canola models} \\

@@

@@

\caption{Summary of parameters for seed canola models} \\

@@

\subsection*{Total yield models}

Formulas for total yield models are  using \texttt{lmer}-style R formulas. Predicted yield for each plant was calculated as: pods per plant $\times$ seeds per pod $\times$ weight per seed. Terms on right side of $\sim$ indicate fixed effects, while terms in brackets indicate random intercepts (and slopes).

\begin{align*}
    \text{Total Yield} \sim & log(\text{Predicted Yield}) + (log(\text{Predicted Yield})|\text{Field}) + \\
    & (log(\text{Predicted Yield})|\text{Plot}), \text{distribution = log-normal} \\
\end{align*}

\begin{table}[h]
\centering\begingroup\fontsize{9}{11}\selectfont
\caption{Summary of parameters for total yield models}

\begin{tabular}{l|l|r|r|r|r|r|r|r|r|r}
\hline
Field Type & Parameter & Mean & SD & Z & median & Min & Max & p-value & N$_{eff}$ & $\hat{R}$\\
\hline
 & Intercept & -0.318 & 0.042 & -7.62 & -0.317 & -0.397 & -0.236 & 0.000 & 982 & 1.000\\
\cline{2-11}
 & Predicted Yield & 1.007 & 0.018 & 55.64 & 1.007 & 0.972 & 1.044 & 0.000 & 1044 & 1.000\\
\cline{2-11}
 & Sigma (field intercept) & 0.119 & 0.041 & 2.89 & 0.112 & 0.051 & 0.216 & 0.004 & 292 & 1.020\\
\cline{2-11}
 & Sigma (field slope) & 0.026 & 0.019 & 1.37 & 0.023 & 0.001 & 0.072 & 0.170 & 295 & 1.013\\
\cline{2-11}
 & Sigma (plot intercept) & 0.389 & 0.037 & 10.47 & 0.388 & 0.318 & 0.465 & 0.000 & 506 & 1.005\\
\cline{2-11}
 & Sigma (plot slope) & 0.169 & 0.017 & 9.86 & 0.168 & 0.135 & 0.204 & 0.000 & 556 & 1.006\\
\cline{2-11}
 & Sigma & 0.253 & 0.008 & 33.30 & 0.253 & 0.239 & 0.268 & 0.000 & 2002 & 1.000\\
\cline{2-11}
 & Correlation (Int:Slope field) & -0.400 & 0.448 & -0.89 & -0.525 & -0.944 & 0.626 & 0.372 & 660 & 1.005\\
\cline{2-11}
\multirow{-9}{*}{\raggedright\arraybackslash Commodity} & Correlation (Int:Slope plot) & -0.989 & 0.007 & -140.44 & -0.990 & -0.998 & -0.972 & 0.000 & 936 & 1.005\\
\cline{1-11}
 & Intercept & -0.210 & 0.072 & -2.90 & -0.210 & -0.348 & -0.066 & 0.004 & 738 & 1.007\\
\cline{2-11}
 & Predicted Yield & 0.856 & 0.025 & 34.62 & 0.856 & 0.806 & 0.904 & 0.000 & 672 & 1.008\\
\cline{2-11}
 & Sigma (field intercept) & 0.040 & 0.018 & 2.28 & 0.038 & 0.011 & 0.079 & 0.022 & 226 & 1.005\\
\cline{2-11}
 & Sigma (field slope) & 0.010 & 0.007 & 1.56 & 0.009 & 0.001 & 0.023 & 0.118 & 217 & 1.005\\
\cline{2-11}
 & Sigma (plot intercept) & 0.097 & 0.013 & 7.26 & 0.097 & 0.072 & 0.124 & 0.000 & 470 & 1.005\\
\cline{2-11}
 & Sigma (plot slope) & 0.032 & 0.005 & 5.83 & 0.032 & 0.021 & 0.043 & 0.000 & 379 & 1.006\\
\cline{2-11}
 & Sigma & 0.289 & 0.012 & 23.59 & 0.289 & 0.266 & 0.314 & 0.000 & 1218 & 1.001\\
\cline{2-11}
 & Correlation (Int:Slope field) & -0.470 & 0.436 & -1.08 & -0.616 & -0.946 & 0.603 & 0.281 & 457 & 1.005\\
\cline{2-11}
\multirow{-9}{*}{\raggedright\arraybackslash Seed} & Correlation (Int:Slope plot) & -0.902 & 0.038 & -23.81 & -0.909 & -0.954 & -0.808 & 0.000 & 486 & 1.007\\
\hline
\end{tabular}
\endgroup{}

\label{tab:totalYieldCoefs}
\end{table}
